Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-20 paper/main.tex
a little prose change near the feature predictive power table

\begin{table}[]
\begin{tabular}{l|l|l}
Feature Name & Feature Category & Feature Predictive Power \\ \hline
F-Size-P & Contextual (Syntactic) & 0.112624 \\
F-Stmt-Constr-C3= & Contextual (Syntactic) & 0.061552 \\
F-Expr-Constr-P=List & Contextual (Syntactic) & 0.054632 \\
F-PythonBlame & Dynamic (Error location) & 0.039189 \\
F-Type=unknown & Dynamic (Type) & 0.037390 \\
F-Type-P=unknown & Contextual (Type) & 0.037330 \\
F-PythonMsg=IndexError & Dynamic (Error message) & 0.032749 \\
F-Size & Syntactic & 0.028203 \\
F-Expr-Constr-P=Dictionary & Contextual (Syntactic) & 0.026663 \\
F-Size-C1 & Contextual (Syntactic) & 0.023662 \\
F-Expr-Constr=Var & Syntactic & 0.020390 \\
F-Type-C1=unknown & Contextual (Type) & 0.019815 \\
\end{tabular}
\caption{Based on the Top-3 Decision Tree on the full dataset. Feature Predictive Power here is the Gini Importance. TODO: add
better-known measure like ANOVA or ReliefF. TODO: base on Top-1 instead?}
\label{tab:feature-predictive-power}
\end{table}

To measure how important each feature is, we use Gini Importance. In a decision
tree,

>>>>

\begin{table}[]
\begin{tabular}{lll}
Name & Category & Gini Importance \\ \bottomrule
Size-P & Contextual (Syntactic)               & 0.112 \\
Stmt-Constr-C3= & Contextual (Syntactic)      & 0.061 \\
Expr-Constr-P=List & Contextual (Syntactic)   & 0.055 \\
PythonBlame & Dynamic (Error location)        & 0.039 \\
Type=unknown & Dynamic (Type)                 & 0.037 \\
Type-P=unknown & Contextual (Type)            & 0.037 \\
PythonMsg=IndexError & Dynamic (Error message)& 0.033 \\
Size & Syntactic                              & 0.028 \\
Expr-Constr-P=Dictionary & Contextual (Syntactic) & 0.027 \\
Size-C1 & Contextual (Syntactic)              & 0.024 \\
Expr-Constr=Var & Syntactic                   & 0.020 \\
Type-C1=unknown & Contextual (Type)           & 0.020 \\
\toprule
\end{tabular}
\caption{Feature predictive power (for a Top-3 Decision Tree 
learned on the entire dataset). 
TODO: add
better-known measure like ANOVA or ReliefF. TODO: base on Top-1 instead?}
\label{tab-feature-predictive-power}
\end{table}

\tabref{feature-predictive-power} summarizes the relative importance 
of the top features in our model. The features are ranked by their
Gini importance (or mean decrease in impurity), a common measure
for decision tree and random forest models~\cite{FIXME}. Informally, the
Gini importance conveys a weighted count of the number of times a feature
is used to split a node: a feature that is learned to guide more model
classification decisions is more important.
